Reproducible Research in R: A Tutorial on how to Do the Same Thing More Than Once

### 2021-11-22 manuscript.Rmd
this is no binary choice

For example, imagine that authors preregistered their intention to include both "working memory" and "fluid intelligence" as covariates in an experimental study, examining the effect of task novelty on reaction time.
When evaluating the planned analyses on the empirical data, these two covariates reveal high collinearity, thus compromising statistical inference.
The authors decide to use PCA to extract common variance related to "intelligence", and include this component as a covariate instead.
This change pertains to an auxiliary assumption (that working memory and fluid intelligence are distinct constructs), but does not undermine the core theory (that task novelty affects reaction time).
Now imagine that a different researcher is interested in the structure of intelligence.
This change to the preregistration directly relates to their theory of intelligence.
That researcher might thus interpret the same result as an explorative finding, suggesting that these aspects of intelligence are unidimensional.
A deviation from preregistration thus requires a judgement about what changes affect the test of the theory [@meehlTheoreticalRisksTabular1978].
Only transparent reporting enables such judgment.

@@

Another common misunderstanding is that preregistration, including PAC, precludes exploratory analyses.
We differentiate between two kinds of exploration, neither of which is limited by PAC.
The first, more traditional kind of exploration involves ad hoc statistical decisions and post hoc explanations of the results.
Such traditional exploratory findings should be explicitly declared in the manuscript to distinguish them from confirmatory findings [@NosekRevolution2018; @nosekPreregistrationHardWorthwhile2019].
The second kind of exploration is through procedurally well defined exploration with exploratory statistical models are standard in machine learning [@brandmaier22mlsem].
These models often involve dozens, if not hundreds of predictors, which makes it difficult to describe them verbally.
With PAC, such models can be preregistered clearly and in comprehensive detail and researcher can therefore precisely calibrate how much they want to explore.
We specifically recommend PAC for such exploratory statistical models.
The merit of preregistration in these cases is to communicate precisely how much exploration was done;
a piece of information that is crucial to assess e.g., whether the results might be overfit [@hastieElementsStatisticalLearning2017, p. 220f.].

>>>>

For example, imagine that authors preregistered their intention to include both "working memory" and "fluid intelligence" as covariates in an experimental study, examining the effect of task novelty on reaction time.
When evaluating the planned analyses on the empirical data, these two covariates reveal high collinearity, thus compromising statistical inference.
The authors decide to use PCA to extract common variance related to "intelligence", and include this component as a covariate instead.
This change pertains to an auxiliary assumption (that working memory and fluid intelligence are distinct constructs), but does not undermine the core theory (that task novelty affects reaction time).
Now imagine that a different researcher is interested in the structure of intelligence.
This change to the preregistration directly relates to their theory of intelligence.
That researcher might thus interpret the same result as an explorative finding, suggesting that these aspects of intelligence are unidimensional.
A deviation from preregistration thus requires a judgement about what changes affect the test of the theory to what extend [@meehlTheoreticalRisksTabular1978].
Only transparent reporting enables such judgment.

@@

Another common misunderstanding is that preregistration, including PAC, precludes exploratory analyses.
We differentiate between two kinds of exploration, neither of which is limited by PAC.
The first, more traditional kind of exploration involves ad hoc statistical decisions and post hoc explanations of the results.
Such traditional exploratory findings should be explicitly declared in the manuscript to distinguish them from confirmatory findings [@NosekRevolution2018; @nosekPreregistrationHardWorthwhile2019].
The second kind of exploration is through procedurally well defined exploration with exploratory statistical models are standard in machine learning [@brandmaier22mlsem].
These models often involve dozens, if not hundreds of predictors, which makes it difficult to describe them verbally.
With PAC, such models can be preregistered clearly and in comprehensive detail and researcher can precisely define a priori how much they want to explore.
We specifically recommend PAC for such exploratory statistical models.
The merit of preregistration in these cases is to communicate precisely how much exploration was done;
a piece of information that is crucial to assess e.g., whether the results might be overfit [@hastieElementsStatisticalLearning2017, p. 220f.].
